\section{Energy source}

In space exploration there exists two sources used for generating power to the space vehicles. One is solar power and the other one is a warm decaying isotope. \newline This part will describe those two types of energy sources.

\subsection{Solar power}

Solar power is produced by solar cells. A solar cell is made of layers of silicon stacked on each other, one layer with a positive charged atoms and other layers is of negative charged atoms. A silicon crystal holds the atoms in a grid shape. When the photons hits the surface of the cell, the photon kicks one electron from the grid on the negative charged side. Then it moves through a wire to the positive charged side, this is where the power is created. When electricity is produced it has to be used or stored in a battery, so it can be saved and used when more power is needed, for example when there is no sun available.\cite{SolarPanels}.\\

\textit{"Most solar panels used in home solar arrays come with a warranty for some 25 or 30 years"}\cite{SolarPanels}
\\
\newline
The solar panels do not wear out easily, meaning it will keep on being a useful energy source for decades.




\subsection{Radioisotope thermoelectric generator}

This method relies on a heating source, which comes from a decaying isotope of plutonium called Pu-238. For converting heat to electricity it uses a method called thermocoupling. Thermocoupling works by having two different metals attached to each other at one end and heating up that end, this will produce a small current.
A radioisotope thermometric generator has an efficiency around 6 to 7\% the rest is still heat and can be used to keep the core of the robot and it's tools warm. The radioisotope thermometric generator method has been used in many space missions and is a very reliable source of energy\cite{RTG}.


